---
title: "Getting Started"
---

### Installation

To install the bspam package, follow the steps below.

1\. Install remotes package, by running the following R code.

```{r eval=F}
if(!requireNamespace("remotes", quietly = TRUE)) install.packages("remotes") 
```

2\. Install bspam by running the following R code.

```{r eval=F}
remotes::install_github("kamataak/bspam")
```

### Optional

`bspam` can implement a fully Bayesian approach for the calibration of model parameters and scoring by using JAGS or Stan. If you desire to use the fully Bayesian estimation, please download JAGS and Stan software on your computer.

To download and install JAGS, download the installation file from <https://sourceforge.net/projects/mcmc-jags/files/JAGS/> as per operating system requirements and follow the installation steps. `bspam` internally uses `runjags` package as an interface to JAGS. `runjags` package needs to be installed separately once JAGS is installed.

Stan can be installed by following the steps explained here: <https://github.com/stan-dev/rstan/wiki/RStan-Getting-Started>. Note that these steps show the installation of `RStan`, which `bspam` uses as an internal package to run Stan code. Please follow the installation steps carefully along with recommended versions of R and RStudio to prevent any issues releated to running Stan with `bspam`.
