---
title: "Scoring 1: Basics"
---

## Overview

In order to estimate latent factor scores and/or WCPM scores, the `scoring()` function needs to be run.

Note that we use the output object `MCEM_run` from the previous passage calibration phase. By default (`type = "general"`), only factor scores ($\theta$ and $\tau$) and their standard errors are reported. By providing an argument `type = "orf"`, WCPM scores and their standard errors are also reported. Also, WCPM scores and/or factor scores, and their standard errors will be estimated for all cases in the data by default.

There are several estimator options and standard error estimation options. Options for the estimator are: maximum likelihood (MLE), maximum a posteriori (MAP), expected a posteriori (EAP), and fully Bayesian approach. Otions for the standard errors are: analytically derived Delta method and simulation-based bootstrap method.

## Preparation

Load required packages.

```{r message=F}
library(tidyverse)
library(bspam)
```

The scoring requires calibration results saved as an object.

```{r calibration2, message=F, cache=T}
MCEM_run1 <- fit.model(data = passage2,
                       person.id = "id.student",
                       task.id = "id.passage",
                       max.counts = "numwords.pass",
                       obs.counts = "wrc",
                       time = "sec",
                       reps.in = 50)
```

## Scoring for All Cases

To estimate WCPM scores for all observations in the data set `passage2`, we use the `scoring()` function as follows. While there are four options for the estimator, this example uses the maximum a posteriori (MAP) estimator. This option is specified by the `est = "map"` argument. Also, the standard errors are estimated by the formula derived by the Delta method, which is specified by the `se = "analytic"` argument. Additionally, the `type = "orf"` argument is specified to estimate the model-based WCPM scores and their standard errors, in addition to the speed and accuracy latent factor scores and their standard errors.

```{r scoring1, message=F, cache=T}
WCPM_all <- scoring(calib.data=MCEM_run1, 
                    data = passage2,
                    person.id = "id.student",
                    occasion = "occasion",
                    group = "grade",
                    task.id = "id.passage",
                    max.counts = "numwords.pass",
                    obs.counts = "wrc",
                    time = "sec",
                    est = "map", 
                    se = "analytic",
                    type="orf")
```

```{r Table1, message=F, cache=T}
knitr::kable(summary(WCPM_all), digits = 2) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

### The Content of Output

In this output, 11 columns were generated. The columns include:

1.  `person.id`

2.  `tau.eap`: EAP estimate of the speed factor scores.

3.  `theta.eap`: EAP estimate of the accuracy factor scores.

4.  `se.tau.eap`: Standard error of the EAP estimate of the speed factor scores.

5.  `se.theta.eap`: Standard error of the EAP estimate of the accuracy factor scores.

6.  `obs.counts.eap`: Estimated counts of correct responses.

7.  `secs.eap`: Estimated time to complete the tasks.

8.  `task.n.wcpm`: The number of tasks to compute the WCPM scores, i.e., the number of passages.

9.  `max.counts.total.wcpm`: The maximum number of total counts to compute WCPM scores, i.e., the number of total words in passages.

10. `wcpm.eap`: EAP estimated WCPM scores.

11. `se.wcpm.eap`: Standard error of the EAP estimated WCPM scores.

## 
