---
title: "Plotting Results"
---

## Overview

The `bspam` package has some functions to plot results from calibration and scoring.

## Preparation

Load required packages.

```{r message=F}
library(tidyverse)
library(bspam)
```

Functions to plot results read an object that contains calibration results or scoring results.

The scoring requires calibration results saved as an object.

```{r calibration2, message=F, cache=T}
MCEM_run1 <- fit.model(data = passage2,
                       person.id = "id.student",
                       task.id = "id.passage",
                       max.counts = "numwords.pass",
                       obs.counts = "wrc",
                       time = "sec",
                       reps.in = 50)
```

```{r scoring1, message=F, cache=T}
WCPM_all <- scoring(calib.data=MCEM_run1, 
                    data = passage2,
                    person.id = "id.student",
                    occasion = "occasion",
                    group = "grade",
                    task.id = "id.passage",
                    max.counts = "numwords.pass",
                    obs.counts = "wrc",
                    time = "sec",
                    est = "map", 
                    se = "analytic",
                    type="orf")
```

## Plot Calibration Results

```{r plot1, message=F, cache=T}
plot.task(MCEM_run1, parameter = "a", sort = TRUE)
```

## Plot Scoring Results

Estimated latent factor scores or model-based WCPM scores can be plotted along with their standard errors.

```{r plot2, message=F, cache=T}
plot.person(WCPM_all, parameter = "wcpm", show.se = TRUE)
```

Estimcated model-based WCPM scores can be plotted along with observed WCPM scores.

```{r plot3, message=F, cache=T, eval=FALSE}
plot.wcpm(WCPM_all)
```

## Plot Information Function

Information function can be plotted.

```{r plot4, message=F, cache=T, eval=FALSE}
plot.information(MCEM_run)
```
