---
title: "Scoring 2: Special Cases"
---

## Overview

In this document, scoring for selected cases and scoring for external task set are presented. We still use the `scoring()` function, but we will need to provide additional information in these scenarios.

## Preparation

Load required packages.

```{r message=F}
library(tidyverse)
library(bspam)
```

Again, the scoring requires calibration results saved as an object. If a calibration result object has not been saved, run a calibration process, such as:

```{r calibration2, message=F, cache=T}
MCEM_run1 <- fit.model(data = passage2,
                       person.id = "id.student",
                       task.id = "id.passage",
                       max.counts = "numwords.pass",
                       obs.counts = "wrc",
                       time = "sec",
                       reps.in = 50)
```

## Scoring for Selected Cases

If the scoring for only selected cases are desired, a list of cases needs to be provided by the cases = argument. The list of cases has to be a one-variable data frame with a variable name `cases`. The format of case values should be: personid_occasion. This one-variable data frame can be created manually, just like shown below. Also, it can be generated by the get.cases() function.

```{r scoring2, message=F, cache=T}
sample.cases <- data.frame(cases = c("2033_fall", "2043_fall", "2089_fall"))
WCPM_sample <- scoring(calib.data = MCEM_run1, 
                       data = passage2,
                       person.id = "id.student",
                       occasion = "occasion",
                       group = "grade",
                       task.id = "id.passage",
                       max.counts = "numwords.pass",
                       obs.counts = "wrc",
                       time = "sec",
                       cases = sample.cases,
                       est = "eap", 
                       se = "analytic",
                       type = "orf")
```

```{r table1, message=F, cache=T}
knitr::kable(summary(WCPM_sample), digits = 2) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

## Scoring for External Task Set

Also, we can specify a set of tasks (i.e., passages) to scale the WCPM scores. If WCPM scores are scaled with a set of passages that is different from the set of passages the student read, the set of passages is referred to as an **external passage set** for the ORF assessment context, or **external task set** in general.

The use of an external passage set is particularly important in the context of ORF assessment to make the estimated WCPM scores to be comparable between students who read different sets of passages, as well as within students for longitudinal data, where a student is likely to read different sets of passages.

```{r scoring3, message=F, cache=T}
WCPM_sample_ext1 <- scoring(calib.data = MCEM_run1, 
                            data = passage2,
                            person.id = "id.student",
                            occasion = "occasion",
                            group = "grade",
                            task.id = "id.passage",
                            max.counts = "numwords.pass",
                            obs.counts = "wrc",
                            time = "sec",
                            cases = sample.cases, 
                            external = c("32004","32010","32015","32016","33003","33037"),
                            est = "eap", 
                            se = "analytic",
                            type = "orf")
summary(WCPM_sample_ext1)
```

## Scoring by Bayesian Approach

A fully Bayesian approach can also be used as an estimator in the `scoring()` function. Note that if `est="bayes"` is specified, there is no need to use the `se=` argument. By default, the standard deviations of the posterior distributions are reported as the standard errors, along with 95% high density intervals, which is analogous to 95% confidence intervals. Here is an example of using the fully Bayesian approach for estimating WCPM scores from the same external passages used in the previous example.

```{r scoring4, message=F, cache=T, eval=FALSE}
WCPM_sample_ext1_bayes <- scoring(calib.data=MCEM_run1, 
                                  data = passage2,
                                  person.id = "id.student",
                                  occasion = "occasion",
                                  group = "grade",
                                  task.id = "id.passage",
                                  max.counts = "numwords.pass",
                                  obs.counts = "wrc",
                                  time = "sec",
                                  cases = sample.cases, 
                                  external = c("32004","32010","32015","32016","33003","33037"),
                                  est = "bayes",
                                  type = "orf")
summary(WCPM_sample_ext1_bayes)
```
