---
title: "Testlet Model"
---

## Overview

When ORF data are collected at the sentence level, sentences are nested within passages and may exhibit local dependence. In this case, a testlet-version of the model can be fitted and scored using `bspam`.

## Example Data Set

The example data set `sentence.level.data` is a sentence-level student data and consisted of reading accuracy and time data for 4 passages from 58 students. The 4 passages were consisted of 4 to 8 sentences, totaling 23 sentences. All 58 students read all 4 passages completely. This is a small subset of the data collected by Nese and Kamata (2014-2018).

\[Insert a bit more about the data?\]

## Calibration

We can use the `fit.model()` function in a similar way to the passage-level calibration. Two additional required arguments to include for testlet model calibration are `sub.task.ed =` and `testlet = TRUE`.

```{r testlet.calb, message=F, cache=T}
Testlet_run <- 
  fit.model(data        = sentence.level.data,
            person.id   = "id.student",
            task.id     = "id.passage",
            sub.task.id = "id.sentence",
            max.counts  = "numwords.sent",
            obs.counts  = "wrc",
            time        = "sec",
            testlet     = TRUE,
            verbose     = TRUE)
```

The estimated testlet parameter is reported as part of the hyper-parameters.

```{r}
Testlet_run$hyper.param
```

Task- and sentence-level parameters can be extracted by:

```{r}
Testlet_run$task.param
```

\[Insert about the results?\]

## Scoring

The scoring by the MAP can be done for this data set by:

```{r}
Testlet_scoring <- 
  scoring(calib.data = Testlet_run,
          data = sentence.level.data,
          person.id = "id.student",
          task.id = "id.passage",
          sub.task.id = "id.sentence",
          obs.counts = "wrc", 
          max.counts = "numwords.sent",
          time = "sec",
          type = "orf",
          testlet = TRUE,
          censoring = TRUE)
```

\[Insert about the results?\]
