---
title: "Scoring for Truncated Response Data"
---

## Overview

In some circumstances, a test may be designed as a speeded test, such that many examinees do not complete all the tasks in the test. For example, a traditional administration of the ORF test limits the student 60 seconds to read aloud the given passage, which is typically consisted of 250 words. In this case, many students do not finish reading the entire passage. The `bspam` R package can score such a data set by the censored model both for the regular and the testlet models.

## Preparation

Load required packages.

```{r message=F}
library(tidyverse)
library(bspam)
```

```{r testlet.calb, message=F, cache=T}
Testlet_run <- 
  fit.model(data        = sentence.level.data,
            person.id   = "id.student",
            task.id     = "id.passage",
            sub.task.id = "id.sentence",
            max.counts  = "numwords.sent",
            obs.counts  = "wrc",
            time        = "sec",
            testlet     = TRUE,
            verbose     = TRUE)
```

## Scoring for Passage-level Data

\[Can we include an example for the passage-level truncated data?\]

## Scoring for Sentence-level Data

Prep

For example, the package includes `sentence.cens.low` and `sentence.cens.high` for demonstrating sentence-level scoring with censored observations. A censored testlet scoring analysis can be run as follows:

```{r censor.score, message=F, cache=T}
Testlet_scoring_cens <- 
  scoring(calib.data = Testlet_run,
          data = sentence.cens.low,
          person.id = "id.student",
          task.id = "id.passage",
          sub.task.id = "id.sentence",
          obs.counts = "wrc",
          max.counts = "numwords.sent",
          time = "sec",
          cens = "cens",
          type = "orf",
          testlet = TRUE,
          censoring = TRUE)
```
